### 2018-09-02 analysis_code/tournament_table.Rmd
update path for analysis code

```{r echo=FALSE,message=FALSE,xtable, results="asis"}
library(dplyr)
library(knitr)
WORKING_PATH <- "/Users/garidor/Desktop/bandits-rl-project"

dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_ht_lhr_3_arms_raw.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(7000)
priors <- as.list(unique(dat['Prior']))$Prior

>>>>

```{r echo=FALSE,message=FALSE,xtable, results="asis"}
library(dplyr)
library(knitr)
WORKING_PATH <- "/Users/garidor/Desktop/CompetingBandits"

#dat <- read.csv(file=paste(WORKING_PATH, "/results/tournament_raw_results/tournament_experiment_ht_lhr_3_arms_raw.csv", sep=""))
dat <- read.csv(file=paste(WORKING_PATH, "/results/free_obs_raw_results/free_obs_experiment_full_sim_no_info_raw.csv", sep=""))
p1_algs <- as.list(unique(dat['P1.Alg']))$P1.Alg
p2_algs <- as.list(unique(dat['P2.Alg']))$P2.Alg
agent_algs <- as.list(unique(dat['Agent.Alg']))$Agent.Alg
time_horizons <-  as.list(unique(dat['Time.Horizon']))$Time.Horizon
time_horizons <- c(2000)
priors <- as.list(unique(dat['Prior']))$Prior
priors <- c("Needle In Haystack")
